Current State of Knowledge Representation Systems for Robotics

### 2011-11-21 paper.tex
Fixed biblio
While here, imported my whole biblio. Easier for now
Started surveying PEIS Ecology.
Added the PEIS architecture diagram, from [Daoutis2009].

While here, added a table of knowledge sources per project

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{supertabular}
\usepackage{pdflscape} %% Used for very big table
\usepackage{moreverb}
\usepackage[table]{xcolor}
\usepackage{listings}
\usepackage{fancyhdr}
\usepackage{fixme}

@@

@@

\begin{tabularx}{\textwidth}{llp{2cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\hiderowcolors
{\bf Name} & {\bf Authors (Institution)} & {\bf Surveyed version} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model} & {\bf Reasoner} \\
\hline
\showrowcolors
{\sc KnowRob} & Tenorth (TU Munich) & & & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom ({\sc Prolog}) \\
ORO & Lemaignan (LAAS-CNRS) & 0.8.0 & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} \\
PEIS Ecology & Saffiotti, Coradeschi \\
 & Kollar, Tellex \\
OMKRF \\
 & Roy, Mavridis \\
 & Wrighteagle \\
 & Vincze \\
 & (Bielfeld) \\
ARMAR & Schmidt-Rohr (Karlsruhe) \\
 & (Saarbrücken) \\
 & Hertzberg (Osnabrück) \\
 & (DFKI Bremen) \\
 (based on {\sc KnowRob} & (JSK) \\
DY-KNOW & Heitnz, Dowerty \\

@@

\end{tabularx}
\end{center}
\caption{List of surveyed systems}
\label{table|surveyed-systems}
\end{table}
\end{landscape}

%\begin{itemize}
%	\item  Saffiotti/Coradeschi
%	\begin{itemize}
%		\item  Grounding, anchoring
%		\item  \emph{PEIS Ecology} (more "SmartHome")
%	\end{itemize}
%
%	\item  Tom Kollar/Stefanie Tellex
%	\begin{itemize}
%		\item  Dialog grounding
%	\end{itemize}
%
%	\item  OMKRF
%	\item  Deb Roy/Nikolaos Mavridis
%	\item  Wrighteagle RoboCup team
%	\item  Markus Vincze (Vienna)
%	\item  Bielefeld
%	\item  Karlsruhe
%	\begin{itemize}
%		\item  ARMAR
%		\item  Sven Schmidt-Rohr
%	\end{itemize}
%
%	\item  Saarbrücken (SemanticMap)
%	\item  Joachim Hertzberg (Osnabrueck)
%	\item  DFKI Bremen
%	\begin{itemize}
%		\item  more "SmartHome"
%	\end{itemize}
%
%	\item  JSK
%	\begin{itemize}
%		\item  KnowRob + physics simulator + planning
%	\end{itemize}
%
%	\item  Frederik Heitnz, Patrick Dowerty
%	\begin{itemize}
%		\item  \emph{DY-KNOW} (stream-based knowledge bases)
%	\end{itemize}
%
%\end{itemize}
%

@@

\bibliographystyle{spbasic}
\bibliography{biblio}

>>>>

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{supertabular}
\usepackage{pdflscape} %% Used for very big table
\usepackage{moreverb}
\usepackage[table]{xcolor}
\usepackage{listings}
\usepackage{fancyhdr}
\usepackage[draft]{fixme}

@@

\graphicspath{{figs/}}

@@

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{lllllll}
\hiderowcolors
{\bf Project} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model} & {\bf Reasoner} & Main reference \\
\hline
\showrowcolors
{\sc KnowRob} & Tenorth (TU Munich) & & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & Lemaignan (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS Ecology & Daoutis, Coradeshi, Loutfi, Saffiotti (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & OWL-Full, 2nd order logics & & \cite{Daoutis2009} \\
 & Kollar, Tellex \\
OMKRF \\
 & Roy, Mavridis \\
 & Wrighteagle \\
 & Vincze \\
 & (Bielfeld) \\
ARMAR & Schmidt-Rohr (Karlsruhe) \\
 & (Saarbrücken) \\
 & Hertzberg (Osnabrück) \\
 & (DFKI Bremen) \\
 (based on {\sc KnowRob} & (JSK) \\
DY-KNOW & Heitnz, Dowerty \\

@@

%\end{tabularx}
\end{tabular}
\end{center}
\caption{List of surveyed systems}
\label{table|surveyed-systems}
\end{table}
\end{landscape}

\subsection{PEIS Ecology}
\label{sect|peis-ecology}

Reference paper:~\cite{Daoutis2009}

{\sc PEIS Ecology}~\cite{Saffiotti2005} is a software \emph{ecosystem} that aim to binds autonomous
robotics with ambient intelligence (network of sensors). \emph{PEIS} stands for
\emph{Physically Embedded Intelligent System}: every robots or intelligent
device in the environment is abstracted as a PEIS.

Each PEIS component is running a \emph{PEIS Kernel} instance. Communication
between instance relies on a custom P2P communication protocol.

In short:
* Roughly the same kind of ambition and architecture.
* Way better than us on the perception side. 
* They try the "2nd order logic" approach. I'd be curious to know what kind of reasoning capability they actually have.
* Their tests are conducted in a static environment. They don't take other agents into consideration (nothing like perspective taking or rich disambiguation).
* No task planning at all (or at least, not discussed in this paper)

More in details:
- object identification based on viewpoint independent SIFT features
- formalized anchoring system that explicitely match percieved attributes to predicates
- Cyc predicates
- ground 12 colors, based on a paper on color perception. Could be useful for us.
- idem, they cite a paper on what spatial relations to compute
- location of objects based on a previously provided semantic map (but not much on this semantic map)
- two "memories": the robot memory stores the current list of percieved objects ; the archive memory stores what is not percieved anymore
- uses directly Cyc (ie, 250 000 common sense concepts...), via CycL language -> 2nd and higher order logics (quantification over predicates, functions, etc)
Remark: using 2nd order logic (ie meta statements), it would be easy to store the knowledge of each agent
- disambiguation in concept name by asking human to decide amongst all concepts known by Cyc
- template based natural language
- experiment conducted in a "smart" indoor environmement + simple robot

\subsubsection{Intrinsic features}
\label{sect|peis-intrinsic-features}

\subsubsection{Integration in the PEIS Ecology architecture}
\label{sect|peis-integration}

\begin{figure}
	\centering
	\includegraphics[width=0.9\columnwidth]{peis-architecture.pdf}
	\caption{The PEIS knowledge representation system, taken from~\cite{Daoutis2009}}
	\label{fig|peis-architecture}
\end{figure}

The PEIS KR\&R system is deeply integrated to the general PEIS Ecology environment.

\begin{table}
\begin{center}
\rowcolors{2}{lightgray}{codegray}

\begin{tabular}{ll}
\hiderowcolors
{\bf Project} & {\bf Common-sense knowledge source} \\
\hline
\showrowcolors
{\sc KnowRob} & {\sc OpenCyc}, processed web content, custom OWL-DL ontology \\
ORO & {\sc OpenCyc}, custom OWL-DL ontology \\
PEIS Ecology & {\sc ReseachCyc} \\
 & Kollar, Tellex \\
OMKRF \\
 & Roy, Mavridis \\
 & Wrighteagle \\
 & Vincze \\
 & (Bielfeld) \\
ARMAR & Schmidt-Rohr (Karlsruhe) \\
 & (Saarbrücken) \\
 & Hertzberg (Osnabrück) \\
 & (DFKI Bremen) \\
 (based on {\sc KnowRob} & (JSK) \\
DY-KNOW & Heitnz, Dowerty \\

\end{tabular}
\end{center}
\caption{Underlying knowledge sources for each project}
\label{table|knowledge-sources}
\end{table}

@@

\bibliographystyle{ieeetr}
\bibliography{biblio}
